Testing Charts: viewers' perceptual accuracy in surveys

### 2023-07-21 SDSS-2023/testing-charts-accuracy.qmd
combination of multiple surveys

We *combine* (rather than cumulate) two surveys $S_1$ and $S_2$, as described in @omuircheartaighCombiningSamplesVs2002, by multiplying weights in $S_1$ and $S_2$ by $\lambda$ and $1 - \lambda$ respectively. $\lambda \in [0,1]$ is given as
$$
\lambda = \frac{n_1/d_1}{n_1/d_1 + n_2/d_2},
$$ where $n_1$ and $n_2$ are the nominal sample sizes and $d_1$ and $d_2$ are the design effects for the estimators.
Here, $d_1$ and $d_2$ are estimated as $$
d_1 = 1 + CV(w_i \in S_1)^2 \ \ \ \text{ and } \ \ \ d_2 = 1 + CV(w_i \in S_2)^2,
$$ where $CV$ is the coefficient of variation of the weights within each sample, and is estimated as in @kishSurveySampling1965 :

>>>>

We *combine* (rather than cumulate) $\ell \ge 2$ surveys $S_1$, $S_2$, ... $S_\ell$ as described in @omuircheartaighCombiningSamplesVs2002, by multiplying weights in $S_i$ by $\lambda_i$, for $1 \le i \le \ell$. $\lambda_i \in [0,1]$ with $\sum_i \lambda_i = 1$ is given as
$$
\lambda_i = \frac{n_i/d_i}{\sum_{j=1}^{\ell}n_j/d_j},
$$ where $n_i$ is the nominal sample of survey $S_i$ and $d_i$ are the design effects for the estimators.
Here, $d_i$ are estimated as 
$$
d_i = 1 + CV(w \in S_i)^2
$$ 
where $CV$ is the coefficient of variation of the weights $w$ within each sample, and is estimated as in @kishSurveySampling1965 :
